---
title: "Pakistan Suicide Bombing Attacks"
author: "Koki Ando"
date: "4/21/2018"
output:
  html_document:
    code_folding: show
    highlight: tango
    number_section: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Analysis about crime data is really interesting thing to me. I have done data analysis about global terrorism dataset.<br/>
1. [Global Terrorism Dataset Shiny Application](https://koki25ando.shinyapps.io/gtd_shinyapp/)<br/>

I believe visualizing about crime history helps people have better understandings about crime and terrorisms.<br/>
Also I think having good understanding about terrorisms has never been mor important in human history.<br/>

So, I hope this article helps you understand a little bit more about crime and terrorism data.

# Code

## Preparation

```{r}
library(data.table)
library(tidyverse)
library(readr)
library(stringr)
library(plotly)
library(scales)

pakistan10 <- read.csv("https://s3-ap-southeast-2.amazonaws.com/koki25ando/PakistanSuicideAttacks+Ver+6+(10-October-2017).csv", stringsAsFactors=FALSE, fileEncoding="latin1")
pakistan11 <- read.csv("https://s3-ap-southeast-2.amazonaws.com/koki25ando/PakistanSuicideAttacks+Ver+11+(30-November-2017).csv", stringsAsFactors=FALSE, fileEncoding="latin1")
```

### Data cleaning
```{r}
pakistan <- bind_rows(pakistan10, pakistan11)
pakistan$Longitude <- as.numeric(pakistan$Longitude)
pakistan$Location.Sensitivity <- as.factor(pakistan$Location.Sensitivity)
pakistan$Injured.Max <- as.numeric(pakistan$Injured.Max)
```

```{r}
pakistan$Target.Type <- str_replace(pakistan$Target.Type, pattern = "civilian", replacement = "Civilian")
pakistan$Target.Type <- str_replace(pakistan$Target.Type, pattern = "foreigner", replacement = "Foreigner")
pakistan$Target.Type <- str_replace(pakistan$Target.Type, pattern = "police", replacement = "Police")
pakistan$Target.Type <- str_replace(pakistan$Target.Type, pattern = "Government official", replacement = "Government Official")
pakistan$Target.Type <- str_replace(pakistan$Target.Type, pattern = "religious", replacement = "Religious")

# Create a date
pakistan <- 
  pakistan %>% 
  select(-S.) %>% 
  separate(Date, sep = "-", into = c("Day", "Date"), extra = "merge")
pakistan$Date <- 
  pakistan$Date %>% 
  str_replace(" ", "-")
pakistan$Date <- pakistan$Date %>% as.Date("%b-%d-%Y")

pakistan$Day <- as.factor(pakistan$Day)

pakistan <- 
  pakistan %>% 
  mutate(Year = year(Date))
```

## Analysis

### Data Component

```{r}
pakistan %>% head()
```

Data itself has many interesting variables such as date, location data.etc...

### Pakistan Map Visualisation

```{r}
world.map <- map_data ("world")
world.map <- world.map %>% filter(region == "Pakistan")
ggplot() + 
  geom_map(data=world.map, map=world.map,
           aes(x=long, y=lat, group=group, map_id=region),
           fill="white", colour="black") + 
  geom_point(data = pakistan, aes(x = Longitude, y = Latitude), colour = "red") + 
  labs(x = "Longitude", y = "Latitude", 
       title = "Pakistan", subtitle ="Where all the attacks happen?")
```

### Where is the Dangerous Zone?

```{r}
pp <- ggplot(as.data.frame(table(pakistan$Province)) %>% 
         arrange(desc(Freq)),
       aes(reorder(Var1, -Freq), Freq, fill = Var1)) + 
  geom_bar(stat = "identity") + 
  labs(x="Province", title = "Top 10 Provinces that experienced most Suicide Bombing Attacks")
ggplotly(pp)
```

KPK Province has experienced by far the most accidents.

### KPK Province's data analysis

```{r}
kpk <- pakistan %>% 
  filter(Province == "KPK")
bp <- kpk %>% 
  ggplot(aes(x = Year, fill = Location.Category)) + 
  geom_bar() +
  labs(title = "Where did Suicide Bombing Attacks in KPK province from 2004 to 2017 happen?", 
       subtitle = "Where did they happen?") +
  scale_fill_discrete(name="Location")
ggplotly(bp)
```

2009 was the peak. And that year, police stations ware the main target.

### Map Visualisation with the sizes of attacks

```{r}
ggplot() + 
  geom_map(data=world.map, map=world.map,
           aes(x=long, y=lat, group=group, map_id=region),
           fill="white", colour="black") + 
  geom_point(data = kpk, aes(x = Longitude, y = Latitude, colour = Injured.Min, size = Killed.Max)) + 
  labs(x = "Longitude", y = "Latitude", size = "Killed", title = "Suicide Bombing Attacks in KPK Province") + 
  scale_colour_gradient(low = "yellow", high = "red", name = "Injured") + 
  xlim(67,74) + 
  ylim(30,35.5)
```

```{r}
bar.plot <- kpk %>% 
  ggplot(aes(x = Year, fill = Target.Type)) + 
  geom_bar() +
  labs(title = "Who were the targets in PKP?", fill = "Target Type")
ggplotly(bar.plot)
```

One thing remarkable is that polices have been main targets.

```{r}
city.p <- ggplot(as.data.frame(table(kpk$City)) %>% 
         arrange(desc(Freq)) %>% head(10),
       aes(reorder(Var1, -Freq), Freq, fill = Var1)) + 
  geom_bar(stat = "identity") + 
  labs(x="City", title = "Which city has experienced the most Attacks?")
ggplotly(city.p)
```

Peshawar has experienced by far the most sucide bombing attacks.<br/>
Now let's focus on the city.

```{r}
peshawar <- kpk %>% filter(City == "Peshawar")
peshawar.p <- peshawar %>% 
  ggplot(aes(Day, fill = Location.Category)) + 
  geom_bar() + 
  scale_x_discrete(limits=c("Sunday", "Monday", "Tuesday", 
                            "Wednesday", "Thursday", "Friday", "Saturday")) + 
  labs(title = "When did attacks happen?")
ggplotly(peshawar.p)
```

Surprisingly, weekend days has experienced less attacks compared to working days.

```{r}
peshawar <- 
  peshawar %>% 
  mutate(Month = month(Date))
peshawar$Month <- as.factor(peshawar$Month)

peshawar.month <- peshawar %>% 
  ggplot(aes(Month)) + 
  geom_bar() +
  scale_x_discrete(labels = c('Jan','Feb','Mar', 'Apr','May','Jun',
                              'Jul','Aug','Sep','Oct','Nov','Dec')) + 
  labs(title = "When did attacks happen?")
ggplotly(peshawar.month)
```

### Who were most targeted?

```{r}
plot_ly(as.data.frame(table(peshawar$Target.Type))[-1,], 
        labels = ~Var1, values = ~Freq, type = 'pie') %>%
  layout(title = 'Who were most targeted in Peshawar?',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```


## Conclusion

Ok, that's it. What i have done in this article was finding <br/>
1. Dangerous zone/city in Pakistan<br/>
2. When thouse attacks happened<br/>
3. People targeted in those places<br/>

Thanks for reading my article.<br/>
Koki

